### 2013-10-01 manuscripts/reply/reply.tex
Fixing typo in figure caption of reply.
Incorporating edits to reply draft.

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Recently, \citet{Oaks2012} presented a simulation-based
    assessment of the approximate Bayesian phylogeographical model choice
    method implemented in \msb, and found the method to lack robustness and
    power to detect temporal variation in divergences that are randomly
    distributed over relatively broad periods of evolutionary history.
    They conclude that a likely mechanism behind the bias toward models with
    few divergence events is the small marginal likelihoods of models with more
    divergence time parameters due to the integration over vast parameter space
    imposed by broad uniform priors characterized by low likelihood and high
    prior density.
    This phenomenon is often referred to as Lindley's paradox
    \citep{Lindley1957}.  \citet{Hickerson2013} have responded to this work,
    criticising the priors used by \citet{Oaks2012} and presenting an
    approximate Bayesian model-averaging approach that uses narrow, empirically
    informed uniform priors.
    \citet{Hickerson2013} conclude this approach circumvents the issues
    revealed by \citet{Oaks2012} and yields robust inference of divergence
    models.
    Furthermore, they argue that the biases revealed by \citet{Oaks2012} are
    inherent to the inefficient rejection algorithm implemented in \msb, rather
    than a result of Lindley's paradox.
    Here we show that the methodology of \citet{Hickerson2013} suffers from a
    fundamental error that renders some of their results invalid and the
    remainder difficult to interpret.
    Furthermore, we demonstrate how the approach of \citet{Hickerson2013} still
    suffers from a bias toward models with less parameter space, which
    manifests in a dangerously strong tendency to sample predominantly from
    models that exclude the true values of the model's parameters.
    Our results suggest that their model-averaged results are dominated by
    models that likely exclude at least some of the true divergence times
    across the 22 pairs of Philippine vertebrates, which adds to the
    difficulty in interpreting their results.
    We also show that in addition to this dangerous behavior, the approach of
    \citet{Hickerson2013} is still strongly biased toward inferring
    simultaneous divergences even when the true divergences are randomly
    distributed over millions of generations.
    Our results, coupled with those of \citet{Oaks2012}, strongly suggest that
    Lindley's paradox is a primary cause of the bias of \msb toward models with
    lesser parameter space.
    We discuss ways to mitigate this bias without resorting to adding an
    additional dimension of model choice to the model or using dangerous
    empirically informed uniform priors.

@@

\noindent Recently, this journal has served as a medium for a
discussion of the potential pitfalls of approximate Bayesian methods of
comparative phylogeographical model choice and prior selection.
The discussion has centered around the approximate Bayesian model choice method,
\msb, which estimates the temporal distribution of divergences among
co-distributed pairs of taxa \citep{Huang2011} by sampling over all
unordered models of divergence.
\citet{Oaks2012} published results of simulation-based power analyses that
revealed that \msb can often be biased towards inferring models of temporally
clustered divergence times among taxon pairs.
\citet{Hickerson2013} published a response to this paper where they present
an empirical Bayes model-averaging approach that they conclude circumvents the
poor behavior of the method revealed by \citet{Oaks2012}.
These papers are largely in agreement with \citet{Hickerson2013} reiterating a
lot of the discussion of
\citet{Oaks2012} regarding the impact of broad uniform priors on Bayesian model
choice.
The main difference in perspectives are centered around
(1) the mechanism by which broad uniform priors cause the poor behavior of
\msb, and
(2) how to potentially ameliorate this issue.

Regarding the mechanism behind the poor behavior of the method,
\citet{Oaks2012} suggest the primary cause is likely the low marginal
likelihoods of parameter-rich models integrated over vast parameter space with
low probability of producing the data, yet relatively high prior density
\citep[this is often referred to as Lindley's paradox;][]{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest the bias is intrinsic to \msb, concluding the
method's rejection algorithm is inefficient and will be increasingly biased as
the overall space of the model increases, either as a function of the number of
taxon pairs or the width of the uniform priors on nuisance parameters.
\citet{Hickerson2013} support their position by giving a probabilistic argument
that focuses on only one of the three prior models used by \citet{Oaks2012}.
We show that this argument is based on an empirical Bayesian approach and
questionable assumptions, and does not explain the bias of the method found in
many of the analyses of \citet{Oaks2012}. 
Furthermore, we present results of additional analyses that, when combined
with the results of \citet{Oaks2012}, strongly suggest that Lindley's paradox
is playing a large role in the poor behavior of \msb.

@@

Regarding perspectives about mitigating the bias, \citet{Oaks2012} suggest that
alternative prior probability distributions on divergence models and nuisance
parameters could reduce the effect of Lindley's paradox.
They also layout simulation-based procedures for determining power, accuracy,
and robustness of the method given a dataset, and recommend any application of
\msb should be accompanied by such procedures, especially if any biological
conclusions are drawn from the results.
Alternatively, \citet{Hickerson2013} present an approximate Bayesian
model-averaging approach for accommodating uncertainty in selecting among
empirically guided priors, and champion the method as a means of avoiding the
pitfalls raised by \citet{Oaks2012}.
We show that fundamental errors in this approach render some of their results
invalid and leave the remaining results difficult to interpret.
Furthermore, we follow the advice of \citet{Oaks2012} and present
simulation-based assessments of Hickerson et al.'s (\citeyear{Hickerson2013})
approach.
Our results demonstrate that the model-averaging approach of
\citet{Hickerson2013} is biased and dangerous.
The approach provides another means by which the model can ``escape'' large
parameter space, and the method's bias toward smaller models remains.
This manifestation of the bias can be dangerous and often excludes the true
parameter space due to the use of narrow uniform priors.
Furthermore we discuss the potential theoretical and practical problems of
empirical Bayesian model choice, which is used and encouraged by
\citet{Hickerson2013} without discussing its potential complications.

%CWL:
%It may be important to point out the error made in their paper, but it can
%also be nit-picky, it depends on how the error impacts the overall message of
%our response.  We should strive to keep the response short and directed at the
%big picture items. If there is a way to still point out the error, then maybe
%some of this section should be used
\section*{An error in Hickerson et al.'s re-analysis of the Philippines data}
\citet{Hickerson2013} re-analyzed the dataset of \citet{Oaks2012} using a
model-averaging approach, where they placed a discrete uniform prior over eight
different prior models (see Table 1 of \citet{Hickerson2013}).
In our initial attempts to explore the behavior of this approach, we found
a fundamental error in the methodology of \citet{Hickerson2013}:
their model mixes different time units.

@@

The fact that their posterior samples are in different units makes the results
of \citet{Hickerson2013} difficult to interpret, and renders their
regression-adjusted results invalid; a fundamental assumption of regression is
that all of the values of the response variable are in the same units.
Thus, the results in sections ``Using ABC Model Comparison to Weight
Alternative Priors for the Philippine Vertebrate Data'' and ``Improved Sampling
Efficiency by Prior Weighting Supports Asynchronous and Recent Divergence for
the Philippines Vertebrate Data'' and presented in Figure 2 of
\citet{Hickerson2013} should be disregarded.
The error is easily illustrated by re-plotting their results with the different
time units indicated (Figure~\ref{figJointPosteriorHickerson}).

% \cwlnote{}{This part seems important, but not related to the error in units
% discussed above}
Another important characteristic of the approach used by \citet{Hickerson2013}
that makes their results difficult to interpret in addition to this error is
their use of narrow, empirically guided uniform priors in an
approximate-Bayesian model-choice framework.
We discuss the dangers of this approach in the next section, and show how the
results of \citet{Hickerson2013} likely exclude true values of the model's
parameters.

@@

\section*{The dangers of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected''. 
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They detail that the limitation in using uniform prior distributions in \msb
necessitates awkward broad priors to avoid excluding the truth, \textit{a
    priori}.
What \citet{Hickerson2013} really mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing both the
prior sensitivity of the method and determining the power of \msb under
real-world conditions with highly informative priors.  
\citet{Oaks2012} discuss
the potential dangers of taking an empirical Bayesian approach to model choice
(see the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}), and we expand on this here by exploring both the theoretical
and practical implications of using empirically informed priors for Bayesian
model choice.

@@

This is not to say that empirical Bayesian approaches are not useful.
Empirical Bayes is a well studied branch of Bayesian statistics that
has given rise to many powerful inference methods.
Unfortunately, empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and misshapen;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
Nevertheless, empirical Bayes methods can provide a powerful means of parameter
estimation that often exhibit favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often exhibit well-behaved frequentist coverage
probabilities
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is unclear.
In Bayesian model choice, the goal is not to estimate parameters, but to
estimate the relative probabilities of candidate models.
Unlike parameter estimates, posterior probabilities represent a summary of the
entire posterior distribution.
Thus, given that empirical Bayesian posterior distributions are not accurate,
there is no guarantee regarding the accuracy of probabilities summarized from
them.

%CWL:
%I like the example, but it may be too cute. It is also too long. I think a
%contrived example is good, but if there could be an example that is more
%relevant to model choice and comparison of inaccurate posterior distributions,
%I think that would be better. This is an example of empirical Bayes, but not
%the potential problem with the use in msbayes. Unless I am interpreting wrong.
%I would be careful about making it to cute as well. You may intend to make it
%easy to understand for a general audience, but it can also seem like talking
%down to Hickerson et al, who we are responding to. It just depends on how you
%read it.
This can be demonstrated with a simple, albeit contrived, example.
Let us say that principal investigator Mary and her new postdoc Will are
interested in the hypothesis that the mass of George Washington's periwig
renders the quarter dollar of the United States unfair.
That is to say their null hypothesis is that the probability of a US
quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
They can certainly evaluate this hypothesis, they can have undergraduate
worker, Joe, flip the coin for them while they tabulate the results.
But being Bayesians, before they call Joe into the lab, they agree on a
prior probability to place on the set of all possible probabilities that
the quarter will land heads when it is flipped.
Given that neither of them have a quarter, and their prior knowledge that Joe
moonlights as a magician, and is notorious for performing coin and card tricks
in the lab, they suspect there is a good chance that the quarter Joe uses will
be either two-headed or two-tailed.
So, knowing that the beta distribution is the conjugate prior for a binomial
likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
(Figure~\ref{figCoinFlip}).

Mary calls Joe into the lab, confirms that he has a quarter, and tells him to
begin flipping it.
After five tosses, four of which was heads, Joe decides that academics are
crazy and leaves the lab to pursue a major in theatre.  Mary and Will, both
being computational biologists, are satisfied with their
empirical dataset of $y = 4$ heads out of $N = 5$ trials.
They know from the conjugacy of the beta prior, that the posterior distribution
has the nice analytical form $\theta|y,N \sim beta(a + y, b + N - y)$, which
in this case is simply $beta(4.5, 1.5)$; this is the true posterior distribution
of $\theta$ given their prior belief and data (Figure~\ref{figCoinFlip}).
This allows them to plug these values into the beta cumulative distribution
function to determine that the posterior probability of their hypothesis is
$p(\theta < 0.5 | y=1, N=5) = 0.088$.
Given their prior belief and dataset, this indeed is the correct posterior
probability of the hypothesis, and Mary and Will should now update their
posterior belief accordingly.

However, reflecting upon the results of their experiment
(Figure~\ref{figCoinFlip}), Mary and Will regret their choice of prior.
Their prior looks very ``poorly selected,'' and if they had only known that the
coin was fair before the data were collected, they would have selected a much
better prior.
Clearly, from their results, they should have used a prior centered
around 0.2; their data suggest a prior of $beta(4.5, 1.5)$ would have been
much ``better.''
Rather than resort to flipping the coin five more times, Mary and Will decide
to redo their analysis using the much better ``prior'' of $p(\theta) \sim
beta(4.5, 1.5)$.
This gives a ``posterior'' of $\theta|y,N \sim beta(8.5, 2.5)$, and a
probability of their hypothesis of $p(\theta < 0.5 | y=1, N=5) = 0.026$.
Now convinced that the US quarter is unfair, albeit not due to the mass of
President Washington's head as they hypothesized, Will begins composing an
e-mail of complaint addressed to the U.S.\ Mint.

If Joe's flips were a representative sample, Mary and Will's empirical Bayes
estimate might very well be a better point estimate for the parameter
\myTheta{}.
However, their empirical Bayes estimate of the probability of their hypothesis
is incorrect and biased.
This simple example shows how parameter estimation is fundamentally different
from estimating the probability of a model.
While empirically informed priors can be used to obtain well-behaved parameter
estimators, using them for model choice is much less certain.
In addition to these theoretical concerns there are practical dangers to
using narrow, empirical, uniform priors for a method that has already
been shown to be biased toward models with lesser parameter space.

\subsection*{Practical dangers of empirically informed uniform priors for
    Bayesian model choice}
% \cwlnote{}{Should this be part of the empirical Bayes section, or something
%     else?}

% \cwlnote{}{It seems like this section can be boiled down to ``empirical Bayes
%     approaches for model choice when using uniform priors can exclude the
%     $truth$ from the prior, which is a violation of Bayes theorem" or something
%     like that. Picking apart what they calculated and we calculated seems like
%     too much detail. I would try to simplify how this is being presented. This
%     can lead into how the use of more appropriate prior distributions should be
%     used.}
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when
using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the prior, because many of the
taxon pairs are expected to have diverged at times older than the upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
Thus, the results of \citet{Hickerson2013} indicate Lindley's paradox is
biasing the method toward models with smaller parameter space, and as a
consequence is biasing the method toward models that exclude the truth (i.e.,
toward estimating model-averaged posteriors dominated by models that exclude
true values of parameters of the model).

%CWL:This should be in the section on model-averaging, not empirical Bayes
%limitations
We explored the propensity of the model-averaging approach of
\citet{Hickerson2013} to exclude the truth in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If Lindley's paradox causes the method to prefer models with less parameter
space, we expect \msb will preferentially sample from this incorrect model
yielding a marginal posterior that is incorrect (i.e., the model-averaged
posterior will be dominated by an incorrect model that excludes the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

>>>>

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Recently, \citet{Oaks2012} presented a simulation-based
    assessment of the approximate Bayesian phylogeographical model choice
    method implemented in \msb, and found the method to lack robustness and
    power to detect temporal variation in divergences that are randomly
    distributed over relatively broad periods of evolutionary history.
    They conclude that a likely mechanism behind the bias toward models with
    few divergence events is the small marginal likelihoods of models with more
    divergence time parameters due to the integration over vast parameter space
    with low likeihood and high prior density that is imposed by broad uniform
    priors.
    \citet{Hickerson2013} have responded to this work, criticising the priors
    used by \citet{Oaks2012} and presenting an approximate Bayesian
    model-averaging approach that uses narrow, empirically informed uniform
    priors.
    \citet{Hickerson2013} use this method to re-analyze the empirical dataset
    of \citet{Oaks2012} comprised of 22 pairs of vertebrate populations from
    the Philippines, and conclude the model-averaging approach circumvents the
    issues revealed by \citet{Oaks2012} and yields robust inference of
    divergence models.
    Furthermore, they argue that the biases revealed by \citet{Oaks2012} are
    inherent to the inefficient rejection algorithm implemented in \msb, rather
    than a result of low marginal likelihoods of parameter-rich models.
    Here we discuss an error in the methodology of \citet{Hickerson2013} that
    renders some of their results invalid and the remainder difficult to
    interpret.
    Furthermore, we demonstrate that the approach of \citet{Hickerson2013} is
    biased toward models with less parameter space, which manifests in a strong
    tendency to sample predominantly from models that exclude the true values
    of the model's parameters.
    Our results suggest that their model-averaged results are dominated by
    models that likely exclude at least some of the true divergence times
    across the 22 pairs of Philippine vertebrates, which adds to the
    difficulty in interpreting their results.
    We also show the approach of \citet{Hickerson2013} is still biased toward
    inferring simultaneous divergences even when the true divergences are
    randomly distributed over millions of generations.
    Our results, coupled with those of \citet{Oaks2012}, strongly suggest that
    low marginal likelihoods of complex models is a primary cause of the bias
    of \msb toward models with less parameter space.
    We discuss ways to mitigate this bias without resorting to adding an
    additional dimension of model choice to the model or using questionable
    empirically informed uniform priors.

@@

\noindent Recently, this journal has served as a medium for a
discussion of the potential pitfalls of approximate Bayesian methods of
comparative phylogeographical model choice and prior selection.
The discussion has centered around the approximate Bayesian model choice method,
\msb, which estimates the temporal distribution of divergences among
co-distributed pairs of taxa \citep{Huang2011} by sampling over all
unordered models of divergence.
\citet{Oaks2012} published results of simulation-based power analyses
showing that \msb can often be biased toward inferring models of temporally
clustered divergence times across taxon pairs.
\citet{Hickerson2013} published a response to this paper where they present
an empirical Bayes model-averaging approach that they conclude circumvents the
poor behavior of the method revealed by \citet{Oaks2012}.
These papers are largely in agreement, with \citet{Hickerson2013} reiterating
much of the discussion of \citet{Oaks2012} regarding the impact of broad
uniform priors on Bayesian model choice.
The main difference in perspectives are centered around
(1) the mechanism by which broad uniform priors cause the poor behavior of
\msb, and
(2) how to potentially mitigate this issue.

\citet{Oaks2012} suggest the primary cause of the poor behavior of the method
is likely the low marginal likelihoods of parameter-rich models integrated over
vast parameter space with low probability of producing the data, yet relatively
high prior density \citep{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest the bias is intrinsic to \msb, concluding the
method's rejection algorithm is inefficient and will be increasingly biased as
the overall space of the model increases, either as a function of the number of
taxon pairs or the width of the uniform priors on nuisance parameters.
\citet{Hickerson2013} support their position by giving a probabilistic argument
that focuses on only one of the three prior models used by \citet{Oaks2012}.
We show that this argument is based on an empirical Bayesian reasoning and
questionable assumptions, and does not explain the bias of the method found in
many of the analyses of \citet{Oaks2012}. 
Furthermore, we present results of additional analyses that, when combined with
the results of \citet{Oaks2012}, strongly suggest small marginal likelihoods of
models with more parameter space is a primary mechanism by which uniform priors
are causing the poor behavior of \msb.

@@

To mitigate the bias, \citet{Oaks2012} suggest alternative prior probability
distributions on divergence models and nuisance parameters could increase the
likelihoods of models with more divergence time parameters.
They also describe simulation-based procedures for determining power, accuracy,
and robustness of the method given a dataset, and recommend any application of
\msb should be accompanied by such procedures.
Alternatively, \citet{Hickerson2013} present an approximate Bayesian
model-averaging approach for accommodating uncertainty in selecting among
empirically guided priors, and champion the method as a means of avoiding the
pitfalls raised by \citet{Oaks2012}.
We discuss errors in this approach that render some of their results invalid
and leave the remaining results difficult to interpret.
Furthermore, we follow the recommendations of \citet{Oaks2012} and present
simulation-based assessments of Hickerson et al.'s (\citeyear{Hickerson2013})
approach.
Our results demonstrate that the model-averaging approach of
\citet{Hickerson2013} is biased toward clustered divergence models and
predisposed to excluding true parameter space.
The model-averaging approach provides another means by which the model can
``escape'' large parameter space, and the method's bias toward smaller models
remains.
This manifestation of the bias often excludes the true parameter space due to
the use of narrow uniform priors.
Furthermore we discuss the potential theoretical and practical problems of
empirical Bayesian model choice.
% which is used and encouraged by
% \citet{Hickerson2013} without discussing its potential complications.

%CWL:
%It may be important to point out the error made in their paper, but it can
%also be nit-picky, it depends on how the error impacts the overall message of
%our response.  We should strive to keep the response short and directed at the
%big picture items. If there is a way to still point out the error, then maybe
%some of this section should be used
\section*{An error in Hickerson et al.'s re-analysis of the Philippines data}
\citet{Hickerson2013} re-analyzed the dataset of \citet{Oaks2012} using a
model-averaging approach, where they placed a discrete uniform prior over eight
different prior models (see Table 1 of \citet{Hickerson2013}).
However, there is a fundamental error in the methodology of
\citet{Hickerson2013}: their model mixes different time units.

@@

The fact that their posterior samples are in different units makes the results
of \citet{Hickerson2013} difficult to interpret, and renders their
regression-adjusted results invalid.
A fundamental assumption of regression is that all of the values of the
response variable are in the same units.
Thus, the results in sections ``Using ABC Model Comparison to Weight
Alternative Priors for the Philippine Vertebrate Data'' and ``Improved Sampling
Efficiency by Prior Weighting Supports Asynchronous and Recent Divergence for
the Philippines Vertebrate Data'' and presented in Figure 2 of
\citet{Hickerson2013} should be disregarded.
The error is easily illustrated by re-plotting their results with the different
time units indicated (Figure~\ref{figJointPosteriorHickerson}).

% \cwlnote{}{This part seems important, but not related to the error in units
% discussed above}
Another important characteristic of the approach used by \citet{Hickerson2013}
that makes their results difficult to interpret is their use of narrow,
empirically guided uniform priors in an approximate-Bayesian model-choice
framework.
We discuss the risks associated with this approach in the next section, and
show how the results of \citet{Hickerson2013} likely exclude true values of the
model's parameters.

@@

\section*{The potential implications of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected.''
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They mention how the use of uniform prior distributions in \msb for many of the
model's parameters necessitates awkward broad priors to avoid excluding the
truth, \textit{a priori}.
What \citet{Hickerson2013} mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing both the
prior sensitivity of the method and determining the power of \msb under
real-world conditions with highly informative priors.  
\citet{Oaks2012} discuss
the potential dangers of taking an empirical Bayesian approach to model choice
(see the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}), and we expand on this here by exploring both the theoretical
and practical implications of using empirically informed priors for Bayesian
model choice.

@@

This is not to say that empirical Bayesian approaches are not useful.
Empirical Bayes is a well studied branch of Bayesian statistics that
has given rise to many powerful inference methods.
However, empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and misshapen;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
Nevertheless, empirical Bayes methods can provide a powerful means of parameter
estimation that often exhibit favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often exhibit well-behaved frequentist coverage
probabilities
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is questionable.
In Bayesian model choice, the goal is not to estimate parameters, but to
estimate the relative probabilities of candidate models.
Unlike parameter estimates, posterior probabilities represent a summary of the
entire posterior distribution.
Thus, given that empirical Bayesian posterior distributions are not accurate,
there is no guarantee regarding the accuracy of probabilities summarized from
them.
In addition to these theoretical concerns there are practical dangers to using
narrow, empirical, uniform priors for a method that has already been shown to
be biased toward models with less parameter space.
% %CWL:
% %I like the example, but it may be too cute. It is also too long. I think a
% %contrived example is good, but if there could be an example that is more
% %relevant to model choice and comparison of inaccurate posterior distributions,
% %I think that would be better. This is an example of empirical Bayes, but not
% %the potential problem with the use in msbayes. Unless I am interpreting wrong.
% %I would be careful about making it to cute as well. You may intend to make it
% %easy to understand for a general audience, but it can also seem like talking
% %down to Hickerson et al, who we are responding to. It just depends on how you
% %read it.
% This can be demonstrated with a simple, albeit contrived, example.
% Let us say that principal investigator Mary and her new postdoc Will are
% interested in the hypothesis that the mass of George Washington's periwig
% renders the quarter dollar of the United States unfair.
% That is to say their null hypothesis is that the probability of a US
% quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
% They can certainly evaluate this hypothesis, they can have undergraduate
% worker, Joe, flip the coin for them while they tabulate the results.
% But being Bayesians, before they call Joe into the lab, they agree on a
% prior probability to place on the set of all possible probabilities that
% the quarter will land heads when it is flipped.
% Given that neither of them have a quarter, and their prior knowledge that Joe
% moonlights as a magician, and is notorious for performing coin and card tricks
% in the lab, they suspect there is a good chance that the quarter Joe uses will
% be either two-headed or two-tailed.
% So, knowing that the beta distribution is the conjugate prior for a binomial
% likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
% (Figure~\ref{figCoinFlip}).

% Mary calls Joe into the lab, confirms that he has a quarter, and tells him to
% begin flipping it.
% After five tosses, four of which was heads, Joe decides that academics are
% crazy and leaves the lab to pursue a major in theatre.  Mary and Will, both
% being computational biologists, are satisfied with their
% empirical dataset of $y = 4$ heads out of $N = 5$ trials.
% They know from the conjugacy of the beta prior, that the posterior distribution
% has the nice analytical form $\theta|y,N \sim beta(a + y, b + N - y)$, which
% in this case is simply $beta(4.5, 1.5)$; this is the true posterior distribution
% of $\theta$ given their prior belief and data (Figure~\ref{figCoinFlip}).
% This allows them to plug these values into the beta cumulative distribution
% function to determine that the posterior probability of their hypothesis is
% $p(\theta < 0.5 | y=1, N=5) = 0.088$.
% Given their prior belief and dataset, this indeed is the correct posterior
% probability of the hypothesis, and Mary and Will should now update their
% posterior belief accordingly.

% However, reflecting upon the results of their experiment
% (Figure~\ref{figCoinFlip}), Mary and Will regret their choice of prior.
% Their prior looks very ``poorly selected,'' and if they had only known that the
% coin was fair before the data were collected, they would have selected a much
% better prior.
% Clearly, from their results, they should have used a prior centered
% around 0.2; their data suggest a prior of $beta(4.5, 1.5)$ would have been
% much ``better.''
% Rather than resort to flipping the coin five more times, Mary and Will decide
% to redo their analysis using the much better ``prior'' of $p(\theta) \sim
% beta(4.5, 1.5)$.
% This gives a ``posterior'' of $\theta|y,N \sim beta(8.5, 2.5)$, and a
% probability of their hypothesis of $p(\theta < 0.5 | y=1, N=5) = 0.026$.
% Now convinced that the US quarter is unfair, albeit not due to the mass of
% President Washington's head as they hypothesized, Will begins composing an
% e-mail of complaint addressed to the U.S.\ Mint.

% If Joe's flips were a representative sample, Mary and Will's empirical Bayes
% estimate might very well be a better point estimate for the parameter
% \myTheta{}.
% However, their empirical Bayes estimate of the probability of their hypothesis
% is incorrect and biased.
% This simple example shows how parameter estimation is fundamentally different
% from estimating the probability of a model.
% While empirically informed priors can be used to obtain well-behaved parameter
% estimators, using them for model choice is much less certain.

\subsection*{Practical concerns about empirically informed uniform priors for
    Bayesian model choice}
% \cwlnote{}{Should this be part of the empirical Bayes section, or something
%     else?}

% \cwlnote{}{It seems like this section can be boiled down to ``empirical Bayes
%     approaches for model choice when using uniform priors can exclude the
%     $truth$ from the prior, which is a violation of Bayes theorem" or something
%     like that. Picking apart what they calculated and we calculated seems like
%     too much detail. I would try to simplify how this is being presented. This
%     can lead into how the use of more appropriate prior distributions should be
%     used.}
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when
using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the limit on the prior, because
many of the taxon pairs are expected to have diverged at times older than the
upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
Thus, the results of \citet{Hickerson2013} indicate that integration over
parameter space with low likelihood is biasing the method toward models with
smaller parameter space, and as a consequence is biasing the method toward
models that exclude the truth (i.e., toward estimating model-averaged
posteriors dominated by models that exclude true values of parameters of the
model).

%CWL:This should be in the section on model-averaging, not empirical Bayes
%limitations
We explored the propensity of the model-averaging approach of
\citet{Hickerson2013} to exclude the truth in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a marginal posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

For our re-analysis of the Philippines dataset we used the model-averaging
approach of \citet{Hickerson2013}, but with a reduced set of prior models to
avoid mixing time units.
We used five prior models, all of which had priors on population sizes of
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim
U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these models had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
We simulated $1\e6$ random samples from each of the models for a total of
$5\e6$ prior samples.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics, standardizing the statistics
using the prior means and standard deviations of the given model.
From the remaining 50,000 samples, we then retained the 10,000 samples with the
smallest Euclidean distance from the observed summary statistics, this time
standardizing the statistics using the prior means and standard deviations
across all five models.
We then repeated this analysis twice, replacing the $M_1$ with
$M_{1A}$ and $M_{1B}$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of at least
some of the 22 taxa, we are nearly certain that these narrower priors are
incorrect and exclude most, if not all, of the divergence times of the
Philippine taxa.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the method's bias toward models with less parameter space,
but rather allows it to manifest in a rather dangerous way.
The method strongly prefers the prior model with the narrowest distribution on
divergence times across all three of our analyses, even when this model is
almost certainly incorrect and excludes the true divergence times of the
Philippine taxa (Table~\ref{tabModelChoiceEmpirical}).
Unfortunately, ``checking'' the priors by plotting the summary statistics from
1000 random samples of each prior model along the first two orthogonal axes of
a principle component analysis, as recommended by \citet{Hickerson2013},
provides no warning of a problem (Figure~\ref{figPCA}).
Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret
(in addition to the error of time units).
